---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidyweo2024spring

<!-- badges: start -->
<!-- badges: end -->

`tidyweo2024spring` is primarily a data package enabling an efficient method for working with [IMF - World Economic Outlook](https://imf.org/en/Publications/SPROLLS/world-economic-outlook-databases#sort=%40imfdate%20descending) in R. 

## Installation

You can install the development version of `tidyweo2024spring` from [GitHub](https://github.com/) with:

``` r
# install the `devtools` package if not yet installed
# install.packages("devtools")

# install tidyweo2024spring from GitHub
devtools::install_github("Teal-Insights/tidyweo2024spring")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r warning=FALSE, message=FALSE}
library(tidyweo2024spring)
library(knitr)
library(tidyverse)
```

```{r}

```
## Available datasets

### IMF - World Economic Outlook by countries
```{r}
imf_countries() %>% 
  head() %>% 
  kable()
```

```{r}

```

### IMF - World Economic Outlook by country groups
```{r}
imf_country_groups() %>% 
  head() %>% 
  kable()
```

```{r}

```
